Ring of Fire Camera Detections Report

### 2023-02-27 analysis/paper/paper.qmd
progress on qmd

```{r, setup, include=FALSE}
knitr::opts_knit$set(root.dir = '~/Documents/WILDLab/rofcamtrap/')
options(scipen = 1, digits = 2)
```

@@

### Sampling protocol

@@

@@

# Hardcoded check
stopifnot(nb_image == 2788375)
```

@@

# Select and distinct down to image-based infos
dets_images <- dets |>  dplyr::select(image_id, max_confidence, isempty) |> 
  dplyr::distinct()

# Breakdown of which images triggered a MD detection
dets_tb <- dets_images$isempty |> table()
dets_tb_sum <- sum(dets_tb)
dets_tb_percent <- dets_tb/dets_tb_sum*100

@@

```{r}
#| label: basics-stats-2
#| echo: false
dets_0 <- dets |> dplyr::filter(confidence > 0)
dets_0.1 <- dets |> dplyr::filter(confidence > 0.1)

# Breakdown of detections by categories (animal, person, vehicles)
dets_tb_cat_unfil <- dets_0 |> dplyr::pull(category_id) |> table()
dets_tb_cat_unfil_sum <- sum(dets_tb_cat_unfil)
dets_tb_cat_unfil_percent <- dets_tb_cat_unfil/dets_tb_cat_unfil_sum*100

@@

# Breakdown of detections above 0.1 by categories (animal, persons, vehicles)
dets_tb_cat <- dets_0.1 |> dplyr::pull(category_id) |> table()
dets_tb_cat_sum <- sum(dets_tb_cat)
dets_tb_cat_percent <- dets_tb_cat/sum(dets_tb_cat)*100

@@

# Histogram of confidence scores above 0.1
dets_0.1 |> 
  dplyr::mutate(category_id = as.character(category_id)) |> 
  dplyr::mutate(Type = dplyr::case_match(category_id,
                                         "0" ~ "Empty",
                                         "1" ~ "Animal",
                                         "2" ~ "Person",
                                         "3" ~ "Vehicle")) |> 
  ggplot2::ggplot() +
  ggplot2::theme_bw() +
  ggplot2::geom_histogram(ggplot2::aes(x=confidence, group=Type, fill=Type),
                          bins = 100) +
  ggplot2::scale_fill_viridis_d() +
  ggplot2::xlab("Confidence Score") +
  ggplot2::ylab("Count")
```

@@

# Number of uploaded images
uploaded <- dets |> dplyr::filter(confidence > 0.1) |> dplyr::pull(image_id) |> 
  unique() |> length()

@@

# Filter for non empty images
anns_wide_noempty <- anns_wide |>
  dplyr::filter(!is.na(to_name))

@@

# Deleted predictions
dels <- anns_wide_noempty |> dplyr::filter(is.na(species))
dels_nb <- nrow(dels)
dels_nb_fmt <- prettyNum(dels_nb, big.mark = ",")
dels_nb_pct <- dels_nb/nrow(anns_wide_noempty)*100

# Should be no manuals here
stopifnot((anns_wide_noempty |> dplyr::filter(is.na(species)) 
           |> dplyr::filter(manual)) == 0)

# Actual annotations
true_anns <- anns_wide_noempty |> dplyr::filter(!is.na(species))
true_anns_nb <- nrow(true_anns)
# true_anns_nb_fmt <- prettyNum(true_anns_nb, big.mark = ",")
# true_anns_nb_pct <- true_anns_nb/processed*100

# Non manuals 
non_mans <- anns_wide_noempty |> dplyr::filter(!is.na(species)) |> 
  dplyr::filter(!manual)
non_mans_nb <- nrow(non_mans)
non_mans_nb_fmt <- prettyNum(non_mans_nb, big.mark = ",")
non_mans_nb_pct <- non_mans_nb/nrow(anns_wide_noempty)*100

# Mans
mans <- anns_wide_noempty |> dplyr::filter(!is.na(species)) |> 
  dplyr::filter(manual)
mans_nb <- nrow(mans)
mans_nb_fmt <- prettyNum(mans_nb, big.mark = ",")
mans_nb_pct <- mans_nb/nrow(anns_wide_noempty)*100

# adjusted
orig_tb <- anns_wide_noempty$origin |> table()
orig_tb_pct <- orig_tb/sum(orig_tb)*100
orig_tb_fmt <- prettyNum(orig_tb, big.mark = ",")
```

@@

```{r}
#| label: quality-control
#| eval: false
#| echo: false

# Only annotations for animals
anns_wide_animals <- anns_wide_noempty %>% 
  filter(species != 'Human') %>% 
  filter(species != 'Vehicle')

# Unknowns and bird breakdown
anns_wide_animals %>% filter(species == "Unknown") %>% pull(id) %>% 
  str_sub(1,4) %>% table() %>% sort()
anns_wide_animals %>% filter(str_detect(species,"Bird")) %>% pull(id) %>% 
  str_sub(1,4) %>% table() %>% sort()

# Join
anns_wide_animals_joined <- anns_wide_animals %>% 
  right_join(info_images, by = "image_id")
```

- Issues with vegetation falsely detected.

@@

```{r}
#| label: species
#| eval: false

# Summary by species

anns_wide_animals_table <- anns_wide_animals %>% 
  mutate(camera_id = anns_wide_animals$id %>% str_split("_") %>% 
           map(~.x[[2]]) %>% unlist()) %>% 
  dplyr::select(camera_id, species) %>% 
  filter(species != "Unknown") %>%
  table() %>% 
  `>`(0) %>% 
  `+`(0) %>% 
  as.data.frame() %>% 
  rownames_to_column("camera_id") %>% 
  arrange(camera_id)
anns_wide_animals_table_tb <- anns_wide_animals_table %>% 
  dplyr::select(-camera_id)
rownames(anns_wide_animals_table_tb) <- anns_wide_animals_table$camera_id

@@

```{r}
#| label: spatial
#| eval: false

RoF_CameraDeploymentLog_WLU <- 
  read_excel("data/raw/WLU_Cameras_Log_2023.xlsx") %>% 
  janitor::clean_names()

RoF_CameraDeploymentLog_WLU_old <- 
  read_excel("data/raw/RoF_CameraDeploymentLog_WLU.xlsx",
             sheet = "Sheet1") %>% 
  janitor::clean_names()

cams_sf <- RoF_CameraDeploymentLog_WLU %>% 
  filter(!is.na(latitude)) %>% 
  filter(!is.na(longitude)) %>% 
  st_as_sf(coords=c("longitude","latitude"), crs="EPSG:4326")
plot(cams_sf$geometry)

lu <- raster("data/raw/CAN_LC_2015_CAL.tif")

lu_dat <- read_csv("data/raw/lu.txt") %>% 
  mutate(cats = as.factor(code))

cams_sf_buffers <- cams_sf %>% 
  st_transform(st_crs(lu)) %>% 
  st_buffer(dist = 1000)

extr <- exact_extract(lu, cams_sf_buffers)

extr_list <- extr %>% 
  lapply(FUN = function(x){
    the_tab <- table(x$value)
    props <- the_tab/sum(the_tab)
    cats <- names(the_tab)
    df <- tibble(cats, props)
  })
names(extr_list) <- cams_sf_buffers$camera_id
extr_table <- bind_rows(extr_list, .id = "camera_id") %>% 
  mutate(props = as.double(props)) %>% 
  left_join(lu_dat, by="cats") %>% 
  dplyr::select(camera_id,category_code, props) %>% 
  # mutate(cats = paste0("cat_", cats)) %>% 
  pivot_wider(names_from = "category_code", values_from = "props") %>% 
  as.data.frame()
extr_table[is.na(extr_table)] <- 0

extr_table_sub <- extr_table %>% 
  filter(camera_id %in% anns_wide_animals_table$camera_id) %>% 
  arrange(camera_id)
extr_table_sub_tb <- extr_table_sub %>% 
  dplyr::select(-camera_id)
rownames(extr_table_sub_tb) <- extr_table_sub$camera_id

# -------------------------------------------------------------------------

# Ordination
all(rownames(anns_wide_animals_table_tb)==rownames(extr_table_sub_tb))
# plot(rda(anns_wide_animals_table_tb,extr_table_sub_tb))

test_rda <- rda(anns_wide_animals_table_tb ~ .,
                extr_table_sub_tb)

sp_scores <- scores(test_rda,
                    choices = 1:2,
                    display = "sp"
)

@@

@@

```{r}
# what commit is this file at? 
if ("git2r" %in% installed.packages() & git2r::in_repository(path = ".")) git2r::repository(here::here())  
```
-->

>>>>

```{r, setup, include=FALSE}
knitr::opts_knit$set(root.dir = '~/Documents/WILDLab/rofcamtrap/')
options(scipen = 1, digits = 2)
library(magrittr)
```

@@

### Camera deployment

@@

```{r}
#| label: spatial
#| echo: false

RoF_CameraDeploymentLog_WLU <- 
  readxl::read_excel(paste0("analysis/data/raw_data/camera_deployments/",
                            "WLU_Cameras_Log_2023.xlsx")) %>% 
  janitor::clean_names()

cams_sf <- RoF_CameraDeploymentLog_WLU %>% 
  dplyr::filter(!is.na(latitude)) %>% 
  dplyr::filter(!is.na(longitude)) %>% 
  sf::st_as_sf(coords=c("longitude","latitude"), crs="EPSG:4326") %>% 
  dplyr::mutate(is_retrieved = is.na(date_retrieved))

# can <- rnaturalearth::ne_countries(country = "Canada", returnclass = "sf") %>% 
#   sf::st_crop(cams_sf)
# 
# can %>% 
#   ggplot2::ggplot() +
#   ggplot2::theme_bw() +
#   ggplot2::geom_sf() +
#   ggplot2::geom_sf(data=cams_sf)

cams_sf %>%
  ggplot2::ggplot() +
  ggplot2::theme_bw() +
  ggplot2::geom_sf(ggplot2::aes(color = is_retrieved))
```

@@

# Hardcoded check
stopifnot(nb_image == 2788375)

exif <- readr::read_csv("analysis/data/raw_data/exif/exif_combined.csv") %>% 
  dplyr::select(-SourceFile) %>% 
  dplyr::mutate(image_id = stringr::str_replace_all(source_file, "/", "_")) %>% 
  dplyr::mutate(image_id = stringr::str_replace_all(image_id, ".JPG", "")) %>% 
  dplyr::mutate(image_id = stringr::str_sub(image_id, 6)) %>% 
  janitor::clean_names()
```

@@

# Select and distinct down to image-based infos
dets_images <- dets %>%  dplyr::select(image_id, max_confidence, isempty) %>% 
  dplyr::distinct()

# Breakdown of which images triggered a MD detection
dets_tb <- dets_images$isempty %>% table()
dets_tb_sum <- sum(dets_tb)
dets_tb_percent <- dets_tb/dets_tb_sum*100

@@

```{r}
#| label: basics-stats-2
#| echo: false
dets_0 <- dets %>% dplyr::filter(confidence > 0)
dets_0.1 <- dets %>% dplyr::filter(confidence > 0.1)

# Breakdown of detections by categories (animal, person, vehicles)
dets_tb_cat_unfil <- dets_0 %>% dplyr::pull(category_id) %>% table()
dets_tb_cat_unfil_sum <- sum(dets_tb_cat_unfil)
dets_tb_cat_unfil_percent <- dets_tb_cat_unfil/dets_tb_cat_unfil_sum*100

@@

# Breakdown of detections above 0.1 by categories (animal, persons, vehicles)
dets_tb_cat <- dets_0.1 %>% dplyr::pull(category_id) %>% table()
dets_tb_cat_sum <- sum(dets_tb_cat)
dets_tb_cat_percent <- dets_tb_cat/sum(dets_tb_cat)*100

@@

# Histogram of confidence scores above 0.1
dets_0.1 %>% 
  dplyr::mutate(category_id = as.character(category_id)) %>% 
  dplyr::mutate(Type = dplyr::case_match(category_id,
                                         "0" ~ "Empty",
                                         "1" ~ "Animal",
                                         "2" ~ "Person",
                                         "3" ~ "Vehicle")) %>% 
  ggplot2::ggplot() +
  ggplot2::theme_bw() +
  ggplot2::geom_histogram(ggplot2::aes(x=confidence, group=Type, fill=Type),
                          bins = 100) +
  ggplot2::scale_fill_viridis_d() +
  ggplot2::xlab("Confidence Score") +
  ggplot2::ylab("Count")
```

@@

# Number of uploaded images
uploaded <- dets %>% dplyr::filter(confidence > 0.1) %>% dplyr::pull(image_id) %>% 
  unique() %>% length()

@@

# Filter for non empty images
anns_wide_noempty <- anns_wide %>%
  dplyr::filter(!is.na(to_name))

@@

# Deleted predictions
dels <- anns_wide_noempty %>% dplyr::filter(is.na(species))
dels_nb <- nrow(dels)
dels_nb_fmt <- prettyNum(dels_nb, big.mark = ",")
dels_nb_pct <- dels_nb/nrow(anns_wide_noempty)*100

# Should be no manuals here
stopifnot((anns_wide_noempty %>% dplyr::filter(is.na(species)) 
           %>% dplyr::filter(manual)) == 0)

# Actual annotations
true_anns <- anns_wide_noempty %>% dplyr::filter(!is.na(species))
true_anns_nb <- nrow(true_anns)
# true_anns_nb_fmt <- prettyNum(true_anns_nb, big.mark = ",")
# true_anns_nb_pct <- true_anns_nb/processed*100

# Non manuals 
non_mans <- anns_wide_noempty %>% dplyr::filter(!is.na(species)) %>% 
  dplyr::filter(!manual)
non_mans_nb <- nrow(non_mans)
non_mans_nb_fmt <- prettyNum(non_mans_nb, big.mark = ",")
non_mans_nb_pct <- non_mans_nb/nrow(anns_wide_noempty)*100

# Mans
mans <- anns_wide_noempty %>% dplyr::filter(!is.na(species)) %>% 
  dplyr::filter(manual)
mans_nb <- nrow(mans)
mans_nb_fmt <- prettyNum(mans_nb, big.mark = ",")
mans_nb_pct <- mans_nb/nrow(anns_wide_noempty)*100

# adjusted
orig_tb <- anns_wide_noempty$origin %>% table()
orig_tb_pct <- orig_tb/sum(orig_tb)*100
orig_tb_fmt <- prettyNum(orig_tb, big.mark = ",")
```

@@

```{r}
#| label: quality-control
#| echo: false

# Only annotations for animals
anns_wide_animals <- anns_wide_noempty %>% 
  dplyr::filter(species != 'Human') %>% 
  dplyr::filter(species != 'Vehicle') %>% 
  dplyr::mutate(camera_id = id %>% stringr::str_split("_") %>% 
                  purrr::map(~.x[[2]]) %>% unlist())

# Unknowns and bird breakdown
anns_wide_animals %>% dplyr::filter(species == "Unknown") %>% 
  dplyr::pull(id) %>% 
  stringr::str_sub(1,4) %>% table() %>% sort() 
anns_wide_animals %>% dplyr::filter(stringr::str_detect(species,"Bird")) %>% 
  dplyr::pull(id) %>% 
  stringr::str_sub(1,4) %>% table() %>% sort()

# Join
anns_wide_animals_joined <- anns_wide_animals %>% 
  dplyr::right_join(dets_images, by = "image_id")
```

The main issue we encountered was a problem in the performances of MegaDetector which caused a lot of false positives, as the model was often tricked by vegetation.

### Analysis

We present a summary of the species identified and an ordination of presence absence data, using proportions of land cover classes observed in a radius of 1 km around each camera location. We used the 2015 Land Cover of Canada dataset.

@@

```{r}
#| label: species
#| echo: false

# Summary by speciesanns_wide_noempty$origin %>% table()

anns_wide_animals_table <- anns_wide_animals %>% 
  dplyr::select(camera_id, species) %>% 
  dplyr::filter(species != "Unknown") %>%
  table() %>% 
  `>`(0) %>% 
  `+`(0) %>% 
  as.data.frame() %>% 
  tibble::rownames_to_column("camera_id") %>% 
  dplyr::arrange(camera_id)
anns_wide_animals_table_tb <- anns_wide_animals_table %>% 
  dplyr::select(-camera_id)
rownames(anns_wide_animals_table_tb) <- anns_wide_animals_table$camera_id
```

@@

```{r}
#| label: extract
#| echo: false

lu_16 <- raster::raster("analysis/data/raw_data/land_use/Class/FarNorth_LandCover_Class_UTM16.tif")
lu_17 <- raster::raster("analysis/data/raw_data/land_use/Class/FarNorth_LandCover_Class_UTM17.tif")

lu_dat <- readr::read_csv("analysis/data/raw_data/land_use/attr_table_northen_ont_lc.txt") %>% 
  dplyr::mutate(cats = as.factor(code))

cams_sf_buffers_16 <- cams_sf %>% 
  sf::st_transform(sf::st_crs(lu_16)) %>% 
  sf::st_buffer(dist = 1000)

cams_sf_buffers_17 <- cams_sf %>% 
  sf::st_transform(sf::st_crs(lu_17)) %>% 
  sf::st_buffer(dist = 1000)

extr_16 <- exactextractr::exact_extract(lu_16, cams_sf_buffers_16)
extr_17 <- exactextractr::exact_extract(lu_17, cams_sf_buffers_17)

ind_16 <- which(lapply(extr_16, function(x) all(is.na(x[,1]))) %>% unlist())
ind_17 <- which(lapply(extr_17, function(x) all(is.na(x[,1]))) %>% unlist())

stopifnot(length(unique(c(ind_16, ind_17))) == length(extr_16))

extr_16[ind_16] <- extr_17[ind_16]

extr <- extr_16

extr_list <- extr %>% 
  lapply(FUN = function(x){
    the_tab <- table(x$value)
    props <- the_tab/sum(the_tab)
    cats <- names(the_tab)
    df <- tibble::tibble(cats, props)
  })
names(extr_list) <- cams_sf_buffers_16$camera_id

extr_table <- dplyr::bind_rows(extr_list, .id = "camera_id") %>% 
  dplyr::mutate(props = as.double(props)) %>% 
  dplyr::left_join(lu_dat, by="cats") %>% 
  dplyr::select(camera_id,category_code, props) %>% 
  tidyr::pivot_wider(names_from = "category_code", values_from = "props") %>% 
  as.data.frame()
extr_table[is.na(extr_table)] <- 0

extr_table_sub <- extr_table %>% 
  dplyr::filter(camera_id %in% anns_wide_animals_table$camera_id) %>% 
  dplyr::arrange(camera_id)
extr_table_sub_tb <- extr_table_sub %>% 
  dplyr::select(-camera_id)
rownames(extr_table_sub_tb) <- extr_table_sub$camera_id

# lu_cropped <- raster::crop(lu_16, cams_sf_buffers_16)
# raster::plot(lu_cropped)
```

```{r}
#| label: ordination
#| echo: false

# Ordination
stopifnot(all(rownames(anns_wide_animals_table_tb)==rownames(extr_table_sub_tb)))

test_rda <- vegan::rda(anns_wide_animals_table_tb ~ .,
                       extr_table_sub_tb)

@@

```{r}
#| label: ordination
#| echo: false

source("scripts/3_ordination.R")

custom_rda_plot(test_rda)
```

### Events definition

```{r}
#| label: ordination
#| echo: false

anns_wide_animals_joined <- anns_wide_animals %>% 
  dplyr::left_join(exif, by = c("source_file", "image_id"))

events_tb <- anns_wide_animals_joined %>% 
  dplyr::filter(species != "Unknown") %>%
  dplyr::mutate(plot_id = stringr::str_sub(id, 1, 4)) %>% 
  dplyr::mutate(date_time = lubridate::ymd_hms(exif_date_time_original,
                                               tz = "Canada/Eastern"),
                year = lubridate::year(date_time),
                month = lubridate::month(date_time),
                day = lubridate::day(date_time),
                ymd = paste(year, month, day, sep = "_")) %>% 
  # dplyr::mutate(ind = paste(species, sex, age, sep = "_")) %>% 
  # dplyr::select(camera_id, image_id, species, ymd) %>% 
  dplyr::select(plot_id, species, ymd) %>% 
  # dplyr::group_by(image_id, ind, ymd) %>% 
  # dplyr::summarise(ind_count=dplyr::n())
  dplyr::distinct() %>% 
  dplyr::group_by(plot_id, species) %>%
  dplyr::summarise(day_count=dplyr::n()) %>% 
  dplyr::ungroup() %>% 
  # dplyr::group_by(camera_id) %>% 
  # dplyr::mutate(day_prop = day_count/sum(day_count)) # %>% 
  tidyr::pivot_wider(values_from = "day_count", names_from = "species") %>%
  dplyr::arrange(plot_id) %>%
  tibble::column_to_rownames("plot_id")

events_tb[is.na(events_tb)] <- 0
events_tb <- events_tb[,colSums(events_tb)>50]
tmp_col <- ncol(events_tb)

# events <- events/rowSums(events)
events <- events_tb %>% 
  tibble::rownames_to_column("plot_id")

### RDA based on events

```{r}
events_tb_cam <- anns_wide_animals_joined %>% 
  dplyr::filter(species != "Unknown") %>%
  dplyr::mutate(plot_id = stringr::str_sub(id, 1, 4)) %>% 
  dplyr::mutate(date_time = lubridate::ymd_hms(exif_date_time_original,
                                               tz = "Canada/Eastern"),
                year = lubridate::year(date_time),
                month = lubridate::month(date_time),
                day = lubridate::day(date_time),
                ymd = paste(year, month, day, sep = "_")) %>% 
  # dplyr::mutate(ind = paste(species, sex, age, sep = "_")) %>% 
  # dplyr::select(camera_id, image_id, species, ymd) %>% 
  dplyr::select(camera_id, species, ymd) %>% 
  # dplyr::group_by(image_id, ind, ymd) %>% 
  # dplyr::summarise(ind_count=dplyr::n())
  dplyr::distinct() %>% 
  dplyr::group_by(camera_id, species) %>%
  dplyr::summarise(day_count=dplyr::n()) %>% 
  dplyr::ungroup() %>% 
  # dplyr::group_by(camera_id) %>% 
  # dplyr::mutate(day_prop = day_count/sum(day_count)) # %>% 
  tidyr::pivot_wider(values_from = "day_count", names_from = "species") %>%
  dplyr::arrange(camera_id) %>%
  tibble::column_to_rownames("camera_id")

events_tb_cam[is.na(events_tb_cam)] <- 0
# events_tb_cam <- events_tb_cam[,colSums(events_tb_cam)>50]
# tmp_col <- ncol(events_tb_cam)

events_rda <- vegan::rda(vegan::decostand(events_tb_cam, "hellinger") ~ .,
                         extr_table_sub_tb)

custom_rda_plot(events_rda, sp_scale = 1.5)
```

```{r}
coords <- cams_sf %>% 
  sf::st_coordinates() %>% 
  as.data.frame()
cams_sf_with_props <- dplyr::bind_cols(cams_sf, coords) %>% 
  sf::st_drop_geometry() %>% 
  dplyr::select(plot_id,X,Y) %>% 
  dplyr::group_by(plot_id) %>% 
  dplyr::mutate(X=mean(X), Y=mean(Y)) %>%
  dplyr::distinct() %>% 
  dplyr::ungroup() %>% 
  dplyr::left_join(events, by = "plot_id")

ggplot2::ggplot() +
  scatterpie::geom_scatterpie(data = cams_sf_with_props,
                              ggplot2::aes(x=X, y=Y, group=plot_id),
                              cols=names(cams_sf_with_props)[4:(4+tmp_col-1)]) + 
  ggplot2::coord_equal() #+ 
  #ggplot2::theme(legend.position = "none")
```

```{r}
zones <- 
  sf::st_read("analysis/data/raw_data/ecozones/ECOREGN/LIO-2022-10-25/ECOREGION.shp") %>% 
  sf::st_transform(crs = sf::st_crs(cams_sf))

plot(zones$geometry)
```

```{r}
zones_filter <- zones %>%
  sf::st_filter(cams_sf)
plot(zones_filter)
```

```{r}
ggplot2::ggplot(zones_filter) +
  ggplot2::theme_bw() +
  ggplot2::geom_sf()
```

```{r}
ggplot2::ggplot(zones_filter) +
  ggplot2::theme_bw() +
  ggplot2::geom_sf() +
  ggplot2::geom_sf(data = cams_sf, cex = 0.5, 
                   ggplot2::aes(col = is_retrieved)) +
  ggplot2::coord_sf(xlim = c(-89, -84),
                    ylim = c(50, 55))
```

```{r}
pols <- sf::st_coordinates(zones_filter) %>% 
  as.data.frame()

regions_labels <- zones_filter %>% 
  sf::st_drop_geometry() %>% 
  dplyr::bind_cols(data.frame(x = c(-85, -85, -87.5),
                              y = c(54, 52, 52.7)))

base <- ggplot2::ggplot() +
  ggplot2::theme_bw()

for (pol in 1:3){
  base <- base + 
    ggplot2::geom_path(data = dplyr::filter(pols, L3 == pol),
                       ggplot2::aes(x=X, y=Y),
                       linewidth = 0.2)
}

base +
  ggplot2::coord_equal(xlim = c(-88, -84.5),
                       ylim = c(50, 54)) +
  ggplot2::geom_label(ggplot2::aes(x=x, y=y, label=ECOREGION), 
                      data = regions_labels) +
  scatterpie::geom_scatterpie(data = cams_sf_with_props,
                              ggplot2::aes(x=X, y=Y, group=plot_id),
                              cols=names(cams_sf_with_props)[4:(4+tmp_col-1)],
                              sorted_by_radius = TRUE,
                              legend_name = "Species",
                              pie_scale = 1.5)
```

```{r}
set.seed(123)
long <- rnorm(50, sd=100)
lat <- rnorm(50, sd=50)
d <- data.frame(long=long, lat=lat)
d <- with(d, d[abs(long) < 150 & abs(lat) < 70,])
n <- nrow(d)
d$region <- factor(1:n)
d$A <- abs(rnorm(n, sd=1))
d$B <- abs(rnorm(n, sd=2))
d$C <- abs(rnorm(n, sd=3))
d$D <- abs(rnorm(n, sd=4))
d[1, 4:7] <- d[1, 4:7] * 3
head(d)
ggplot2::ggplot() + scatterpie::geom_scatterpie(ggplot2::aes(x=long, y=lat, group=region), data=d,
                           cols=LETTERS[1:4]) + ggplot2::coord_equal()
```

@@

```{r}
# what commit is this file at? 
if ("git2r" %in% installed.packages() & git2r::in_repository(path = ".")) git2r::repository(here::here())  
```

```{r}
# -------------------------------------------------------------------------

# # Create ordered dataframe, and calculate time interval between images.
# x1 <- x %>%
#   # Sometimes VNA sneaks in here
#   mutate(number_individuals = as.numeric(ifelse(number_individuals == "VNA", 1, number_individuals))) %>%
#   # Amalgamate tags of same species in same image; currently broken into two separate rows
#   group_by(location, {{datetime_col}}, common_name) %>%
#   mutate(number_individuals = sum(number_individuals)) %>%
#   distinct(location, {{datetime_col}}, common_name, number_individuals, .keep_all = TRUE) %>%
#   ungroup() %>%
#   # Order the dataframe
#   arrange(project, location, {{datetime_col}}, common_name) %>%
#   group_by(project, location, common_name) %>%
#   # Calculate the time difference between subsequent images
#   mutate(interval = int_length({{datetime_col}} %--% lag({{datetime_col}}))) %>%
#   # Is this considered a new detection?
#   mutate(new_detection = ifelse(is.na(interval) | abs(interval) >= threshold, TRUE, FALSE)) %>%
#   ungroup() %>%
#   # Number independent detections
#   mutate(detection = c(1, cumsum(new_detection[-1]) + 1))
# 
# # Summarise detections
# x2 <- x1 %>%
#   group_by(detection, project, location, common_name, scientific_name) %>%
#   summarise(start_time = min({{datetime_col}}),
#             end_time = max({{datetime_col}}),
#             total_duration_seconds = int_length(start_time %--% end_time),
#             n_images = n(),
#             avg_animals = mean(number_individuals),
#             max_animals = max(number_individuals))
```

-->
